---
title: "Kan_Raw_Processed"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r}
library(tidyverse)
library(osfr)
library(readxl)
```

# Load custom functions

```{r}
source("utils.R")
```

# Download data from OSF
## OSF auth (until project is public)

Read/write token should be created on OSF and it should be named as "osf_token_write"

```{r osf authentication}
osf_auth(token = read_lines(list.files(pattern ="osf_token_write_.*.txt")))
```

## Connect to data OSF folder
```{r osf connect to OSF folder, message = FALSE}
data_guid <- ""

kan_project <- osf_retrieve_node(data_guid)
```

## Download data locally

```{r osf download data, message = FALSE, echo = T, results = "hide"}
# Save data path in the project repository
local_data_pth <- file.path("Data","Raw")

# Create local data structure if it is missing
create_local_structure(local_data_pth)

# TODO: Rewrite this part if there are data uploaded
# List datafiles on OSF
data_files <- 
  kan_project %>% 
  osf_ls_files() %>% 
  filter(name == "Processed") %>% 
  osf_ls_files() 

data_files %>% 
  group_by(name) %>% # for each experiment type
  do(download_files(.,local_data_pth))

# uncomment following line to remove the data   
# remove_local_data(local_data_pth)
```

# Exp 1
## Read files

Read datafile from the subfolder of the given experiment.

```{r}
raw <- read_tsv("Data/Raw/Exp1/Kan_Raw_Exp1_data.tsv")
```

## Selecting only needed variables

Opensesame logs several variables that are not needed for further analysis. For the sake of simplicity, we only keep the variables that are needed.

```{r}
raw <-
  raw %>%
  select(filename,
         lab,
         count_trial_decider,
         live_row,
         live_row_practice_loop,
         procedure,
         stim_type,
         stimulus,
         stim_color,
         conflict_condition,
         correct,
         correct_response,
         correct_stroop_input,
         critical_area,
         datetime,
         response,
         response_stroop_input,
         response_keyboard_input,
         response_keyboard_input_1,
         response_keyboard_input_2,
         response_keyboard_input_3,
         response_time,
         response_time_stroop_input,
         response_time_keyboard_input,
         response_time_keyboard_input_1,
         response_time_keyboard_input_2,
         response_time_keyboard_input_3,
         count_end_sent_logger,
         count_sentence,
         count_start_sentence,
         count_stroop_input,
         count_stroop_sequence,
         acc,
         avg_rt)
```

## Dividing parts of the experiment into different tables
### Practice trials

```{r}
practice_raw <-
  raw %>%
  filter(is.na(procedure) & is.na(stim_type))
```

### Baseline stroop trials

```{r}
baseline_raw <-
  raw %>% 
  filter(is.na(procedure) & !is.na(stim_type))
```

### Practice with Stroops and sentences trials

```{r}
practice_sent_stroop_raw <-
  raw %>% 
  filter(!is.na(procedure) & is.na(count_trial_decider))
```

### Test trials

```{r}
test_raw <- 
  raw %>% 
  filter(!is.na(count_trial_decider)) %>% 
  select(-count_trial_decider,
         -live_row_practice_loop,
         -acc,
         -avg_rt,
         -contains("count_"),
         -correct_stroop_input)
```

## Read specification of the stimuli for the test trials

```{r}
test_trial_spec <- read_xlsx("exp1_test_trial_spec.xlsx", sheet = 1)
```

## Creating variables for the ets trials

```{r}
test_raw <-
  test_raw %>% 
  rename(trial_id = live_row,
         participant_id = File) %>% 
  mutate(response_keyboard_input_3 = case_when(trial_id %in% (test_trial_spec$trial_id + 1) ~ response_keyboard_input_3,
                                               TRUE ~ NA_character_),
         response_time_keyboard_input_3 = case_when(!is.na(response_keyboard_input_3) ~ response_time_keyboard_input_3,
                                                    TRUE ~ NA_integer_))

setdiff(
test_raw %>% 
  filter(!is.na(response_keyboard_input_3)) %>% 
  pull(trial_id),
test_trial_spec %>% 
  mutate(trial_id = trial_id + 1) %>% 
  pull(trial_id)
)

sentence_last_word_responses <-
  test_raw %>% 
  select(trial_id,
         participant_id,
         Subdirectory,
         response_keyboard_input_3,
         response_time_keyboard_input_3) %>% 
  mutate(response = response_keyboard_input_3,
         response_time = response_time_keyboard_input_3) %>% 
  select(-response_keyboard_input_3, -response_time_keyboard_input_3) %>% 
  drop_na(response) %>% 
  mutate(trial_id = trial_id - 1) %>% 
  left_join(., test_trial_spec, by = "trial_id")

test_raw <- 
  test_raw %>% 
  bind_rows(sentence_last_word_responses) %>% 
  arrange(participant_id, trial_id) %>%
  mutate(correct = as.integer(correct),
         correct = case_when(is.na(correct) & response == correct_response ~ 1L,
                             is.na(correct) & response != correct_response ~ 0L,
                             TRUE ~ correct))
```

## Exploratory data analysis
### Number of practice and test trials per participant before exclusion

```{r}
raw %>%
  mutate(test_trial = case_when(test_trial == 0L ~ "practice trial",
                                test_trial == 1L ~ "test trial",
                                TRUE ~ NA_character_)) %>% 
  group_by(subject_nr, test_trial) %>%
  count()
```

## Testing the consistency of the data

Should we test whether all of the experiments were run on full screen?
the same for opensesame version

The four digit code in the filename that is saved in the [filename] variable should match the content of the [subject_nr] variable.

```{r}

```

# Exp 2
## Read files

Read datafile from the subfolder of the given experiment.

```{r}
raw <- read_tsv("Data/Raw/Exp2/Kan_Raw_Exp2_data.tsv")
```

## Selecting only needed variables

Opensesame logs several variables that are not needed for the further analysis. For the sake of simplicity, we only keep the variables that are needed.

```{r}
raw <-
  raw %>%
  select(live_row,
         live_row_practice_loop2,
         loop_num,
         count_Blank,
         count_Stimulus,
         count_decider,
         count_down_neck_stim,
         count_up_neck_stim,
         count_inco_neck_exp2_script,
         count_incongruent_necker,
         count_keyboard_input,
         count_necker_keyboard_input,
         count_left_necker,
         count_right_necker,
         count_neck_logger,
         count_stroop_sequence,
         count_stroop_logger,
         procedure,
         conflict_condition,
         stim_color,
         stim_type,
         stimulus,
         correct,
         correct_response,
         response,
         response_keyboard_input,
         response_necker_keyboard_input,
         response_time_keyboard_input,
         response_time_necker_keyboard_input,
         response_time,
         keypress,
         time_trial_loops,
         time_Blank,
         time_Fixation,
         time_BaselineLoop,
         time_Stimulus,
         time_decider,
         time_down_neck_stim,
         time_inco_neck_exp2_script,
         time_incongruent_necker,
         time_keyboard_input,
         time_left_necker,
         time_neck_logger,
         time_necker_keyboard_input,
         time_practice_loop2,
         time_right_necker,
         time_stroop_logger,
         time_stroop_sequence,
         time_up_neck_stim,
         time_down_neck_stim,
         time_Instructions_1,
         time_Instructions_2,
         time_Instructions_3,
         time_Instructions_4,
         time_Instructions_5,
         time_Instructions_6,
         time_Instructions_7,
         acc,
         avg_rt,
         datetime,
         File,
         Subdirectory)
```

## Divide the datatable according to experiment parts
### Practice trials

```{r}
# Read practice trial specifications
prac_trial_spec <- read_csv2("practice_trial_spec.csv")

# Practice trials
raw_practice <- 
  raw %>%
  mutate(trial_id = live_row_practice_loop2,
         participant_id = str_remove_all(File, ".*/|.csv")) %>% 
  group_by(participant_id, trial_id) %>% 
  mutate(trial_id_nr_instances = row_number()) %>% 
  ungroup() %>% 
  filter(trial_id_nr_instances == 1) %>% 
  select(trial_id,
         participant_id,
         Subdirectory,
         procedure,
         conflict_condition,
         stim_color,
         stim_type,
         stimulus,
         correct,
         correct_response,
         response,
         keypress,
         response_keyboard_input,
         response_necker_keyboard_input,
         response_time_necker_keyboard_input,
         response_time) %>% 
  mutate(conflict_condition = case_when(is.na(conflict_condition) ~ "IC",
                                        TRUE ~ conflict_condition),
         stim_color = case_when(procedure == "neck_con_r" ~ "black",
                                TRUE ~ stim_color),
         stimulus = case_when(procedure == "neck_con_r" ~ NA_character_,
                                TRUE ~ stimulus),
         correct_response = case_when(procedure == "neck_con_r" ~ "f",
                                TRUE ~ correct_response),
         response = case_when(procedure == "neck_con_r" ~ response_necker_keyboard_input,
                                TRUE ~ response),
         correct = case_when(procedure == "neck_con_r" & response == correct_response ~ 1,
                             procedure == "neck_con_r" & response != correct_response ~ 0,
                             TRUE ~ correct),
         response_necker_keyboard_input = case_when(trial_id == 3 ~ response_necker_keyboard_input,
                                                    trial_id == 7 ~ response_necker_keyboard_input,
                                                    trial_id == 11 ~ response_necker_keyboard_input,
                                                    TRUE ~ NA_character_),
         response_time_necker_keyboard_input = case_when(!is.na(response_necker_keyboard_input) ~ response_time_necker_keyboard_input,
                                                         TRUE ~ NA_real_))

cong_necker_trial_responses <-
  raw_practice %>% 
  select(trial_id,
         participant_id,
         Subdirectory,
         response_necker_keyboard_input,
         response_time_necker_keyboard_input) %>% 
  mutate(response = response_necker_keyboard_input,
         response_time = response_time_necker_keyboard_input) %>% 
  select(-response_necker_keyboard_input, -response_time_necker_keyboard_input) %>% 
  drop_na(response) %>% 
  mutate(trial_id = trial_id - 1) %>% 
  left_join(., prac_trial_spec, by = "trial_id")

raw_practice <- 
  raw_practice %>% 
  bind_rows(cong_necker_trial_responses) %>% 
  arrange(participant_id, trial_id) %>% 
  mutate(correct = case_when(is.na(correct) & response == correct_response ~ 1,
                             is.na(correct) & response != correct_response ~ 0,
                             TRUE ~ correct))

raw_practice %>% 
  filter(procedure %in% c("neck_con_r", "neck_con_l")) %>% 
  group_by(participant_id) %>% 
  summarise(sum_correct = sum(correct),
            acc = sum_correct / 4 * 100) %>% 
  group_by(acc) %>% 
  count()
```

### Stroop baseline

```{r}
raw_baseline <-
  raw %>%
  filter(procedure == "neck_con_r") %>% 
  select(File,
         procedure,
         conflict_condition,
         stim_color,
         stim_type,
         stimulus,
         correct,
         correct_response,
         response,
         response_time)
```

```{r}
raw_baseline_accuracy <- 
  raw_baseline %>% 
  group_by(File, correct) %>% 
  summarise(N = n()) %>% 
  group_by(File) %>% 
  mutate(sum_N = sum(N),
         freq = N / sum_N * 100) %>% 
  ungroup()
```

```{r}
raw_baseline_accuracy %>% 
  filter(correct == 0) %>% 
  ggplot() +
  aes(x = N) +
  geom_bar() +
  scale_x_continuous(limits = c(0, 55),
                     breaks = c(0, 10, 20, 30, 40, 54),
                     labels = c(0, 10, 20, 30, 40, 54))
```

```{r}
raw_baseline_accuracy %>% 
  filter(correct == 0,
         freq >= 30) %>%
  count()
```

### Test trials 

```{r}
# Read practice trial specifications
test_trial_spec_loop_0 <- read_xlsx("test_trial_spec_loop_0.xlsx", sheet = 1)
test_trial_spec_loop_1 <- read_xlsx("test_trial_spec_loop_1.xlsx", sheet = 1)
test_trial_spec_loop_2 <- read_xlsx("test_trial_spec_loop_2.xlsx", sheet = 1)
test_trial_spec_loop_3 <- read_xlsx("test_trial_spec_loop_3.xlsx", sheet = 1)
test_trial_spec_loop_4 <- read_xlsx("test_trial_spec_loop_4.xlsx", sheet = 1)
test_trial_spec_loop_5 <- read_xlsx("test_trial_spec_loop_5.xlsx", sheet = 1)

# Practice trials
raw_test <- 
  raw %>%
  mutate(trial_id = live_row,
         participant_id = str_remove_all(File, ".*/|.csv")) %>% 
  filter(!is.na(loop_num)) %>% 
  select(trial_id,
         participant_id,
         Subdirectory,
         loop_num,
         procedure,
         conflict_condition,
         stim_color,
         stim_type,
         stimulus,
         correct,
         correct_response,
         response,
         keypress,
         response_keyboard_input,
         response_necker_keyboard_input,
         response_time_necker_keyboard_input,
         response_time) %>% 
  mutate(conflict_condition = case_when(is.na(conflict_condition) ~ "first_trial",
                                        TRUE ~ conflict_condition),
         stim_color = case_when(procedure == "neck_con_r" ~ "black",
                                TRUE ~ stim_color),
         stimulus = case_when(procedure == "neck_con_r" ~ NA_character_,
                                TRUE ~ stimulus),
         correct_response = case_when(procedure == "neck_con_r" ~ "f",
                                TRUE ~ correct_response),
         response = case_when(procedure == "neck_con_r" ~ response_necker_keyboard_input,
                                TRUE ~ response),
         correct = case_when(procedure == "neck_con_r" & response == correct_response ~ 1,
                             procedure == "neck_con_r" & response != correct_response ~ 0,
                             TRUE ~ correct),
         response_necker_keyboard_input = case_when(trial_id == 3 ~ response_necker_keyboard_input,
                                                    trial_id == 7 ~ response_necker_keyboard_input,
                                                    trial_id == 11 ~ response_necker_keyboard_input,
                                                    TRUE ~ NA_character_),
         response_time_necker_keyboard_input = case_when(!is.na(response_necker_keyboard_input) ~ response_time_necker_keyboard_input,
                                                         TRUE ~ NA_real_))

cong_necker_trial_responses <-
  raw_practice %>% 
  select(trial_id,
         participant_id,
         Subdirectory,
         response_necker_keyboard_input,
         response_time_necker_keyboard_input) %>% 
  mutate(response = response_necker_keyboard_input,
         response_time = response_time_necker_keyboard_input) %>% 
  select(-response_necker_keyboard_input, -response_time_necker_keyboard_input) %>% 
  drop_na(response) %>% 
  mutate(trial_id = trial_id - 1) %>% 
  left_join(., prac_trial_spec, by = "trial_id")

raw_practice <- 
  raw_practice %>% 
  bind_rows(cong_necker_trial_responses) %>% 
  arrange(participant_id, trial_id) %>% 
  mutate(correct = case_when(is.na(correct) & response == correct_response ~ 1,
                             is.na(correct) & response != correct_response ~ 0,
                             TRUE ~ correct))

raw_practice %>% 
  filter(procedure %in% c("neck_con_r", "neck_con_l")) %>% 
  group_by(participant_id) %>% 
  summarise(sum_correct = sum(correct),
            acc = sum_correct / 4 * 100)
```

```{r}
# raw <-
#   raw %>% 
#   mutate(experiment_part = case_when(procedure == "neck_con_r" ~ "baseline_loop",),
#          procedure = case_when(procedure == "neck_con_r" ~ "stroop",
#                                TRUE ~ procedure))
```